### 2018-01-23 Sections/entanglement_the_ultimate_quantum_resource.tex
Figures for satellite entanglement distribution down/uplink

So which ought our quantum hubs specialise in, entanglement distribution, entangling measurements, or both? For most practical purposes the former is far more powerful and robust. Let us take the example of fusing two remote cluster states together to form a larger virtual cluster. Imagine that their fusion operations are optically mediated by a satellite overhead. The options for state fusion are:
\begin{itemize}
	\item The satellite uses the downlink to distribute an entangled Bell-pair between the two nodes. Each node performs a Bell projection between their half of the Bell-pair and their respective qubit from their local cluster state, creating a link.
	\item Each node entangles their cluster state qubit with an optical qubit, which is uplinked to the satellite. The satellite performs a Bell projection between the two received optical qubits, thereby implementing entanglement swapping between the two nodes, creating a link.
\end{itemize}

>>>>

So which ought our quantum hubs specialise in, entanglement distribution, entangling measurements, or both? For most practical purposes the former is far more powerful and robust. Let us take the example of fusing two remote cluster states together to form a larger virtual cluster. Imagine that their fusion operations are optically mediated by a satellite overhead. The options for state fusion are:
\begin{itemize}
	\item The satellite uses the downlink to distribute an entangled Bell-pair between the two nodes. Each node performs a Bell projection between their half of the Bell-pair and their respective qubit from their local cluster state, creating a link. See Fig.~\ref{fig:sat_up_down}(a).
	\item Each node entangles their cluster state qubit with an optical qubit, which is uplinked to the satellite. The satellite performs a Bell projection between the two received optical qubits, thereby implementing entanglement swapping between the two nodes, creating a link. See Fig.~\ref{fig:sat_up_down}(b).
\end{itemize}

\begin{figure}[!htb]
	\includegraphics[width=0.47\textwidth]{satellite_downlink_uplink}
	\caption{Satellite-mediated cluster state fusion operations for creating a link between two cluster states held by distant ground nodes. (a) Via entanglement distribution over a downlink channel. (b) Via distributed Bell projection over an uplink channel. When performing a distributed Bell measurement it is essential that the optical qubits arrive synchronously at the entangling measurement device (e.g a PBS), which is technologically challenging to implement on satellite given the unpredictable nature of the atmospheric quantum channel, necessitating on-board quantum memories to synchronise the qubits.} \label{fig:sat_up_down}
\end{figure}
